---
title: "Weight of Fish"
author: "Taelynn Condoll"
date: "summer 2022"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)

Fish = read.csv("Fish.csv")
Perch = filter(Fish, Species == "Perch")
Pike = filter(Fish, Species == "Pike")
Roach = filter(Fish, Species == "Roach")
```

# Predicting Fish Weight
``` {r}
pwt = lm(Weight~ Length1+ Length2+ Length3 + Height,data =Perch)
summary(pwt)
```

## Perch
```{r}

pwt =  lm(Weight~ Length1 + Length2 + Length3 + Height, data = Perch)
summary(pwt)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ Length1+ Length2 + Length3 + Height,
               data = Perch,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
regsubsets.out
```

```{r}
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```
### Best Models

The best model would be 4(1) because it fills the most columns

### Best Two regressor model

The best two regressor uses length 3 and Height. 

## Pike
```{r}

pwt =  lm(Weight~ Length1 + Length2 + Length3 + Height, data = Pike)
summary(pwt)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ Length1+ Length2 + Length3 + Height,
               data = Pike,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
regsubsets.out
```

```{r}
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```
### Best Models

The best model is 4(1) because it fills the most columns.

### Best Two regressor model

The best two regressor model uses Length 1 and Length 3.

## Roach
```{r}

pwt =  lm(Weight~ Length1 + Length2 + Length3 + Height, data = Roach)
summary(pwt)
```

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ Length1+ Length2 + Length3 + Height,
               data = Roach,
               nbest = 2,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
regsubsets.out
```

```{r}
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```
### Best Models

The best model is regressor 4(1) because it checks all of the boxs.

### Best Two regressor model

The best two regressor model is length 1 and length 3

## Final Summary Statements
For Perch The best model would be 4(1) because it fills the most columnsaand the best two regressor uses length 3 and Height. For pike the best model is 4(1) because it fills the most columns.The best two regressor model uses Length 1 and Length 3. And lastly The best model is regressor 4(1) because it checks all of the boxs and the best two regressor model is length 1 and length for roach 3.